|

### 2024-08-07 doc/paper.qmd
pulled and prepared data

## delete. from mine
# List of Abbreviations
\setlength{\parindent}{0em}

@@

The replicated table is shown below, followed by a detailed comparison, replication steps documentation, and discussion of the results.

## delete from fikir. 1st table is for original table
```{python}
#| echo: false
#| output: asis

print(prep_latex_table(
    results['penman_table'],
    caption='Original table Penman 2013 - P/B Ratios And Future Residual Income',
    label='tab:original_penman'
))
```

@@

In addition, I impose the following assumptions to ensure clarity and consistency where the paper does not provide explicit guidance:

1. The original paper references the November 2000 version of the Worldscope Database. However, the data used for this analysis represents the latest available version, updated in July 2024, with quarterly frequency updates [@WRDS_2024]. Due to potential adjustments and updates made to the database since November 2000, there may be differences between the databases that could affect the results. For example, companies may restate financials after the original reporting period, so that these restatements are reflected in the later database version rather than the historical one. Moreover, the data vendor Refinitiv regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the November 2000 snapshot.
2. The original paper outlines key terms that will be used in this project to ensure consistency and accuracy in the replication. @Leuz_2003 define earnings management as the manipulation of a firm's reported economic performance by insiders to deceive certain stakeholders or to affect contractual results. Authors describe investor protection as a key institutional factor that limits insiders' acquisition of private control benefits, thereby reducing their incentives to manage accounting earnings by ensuring strong and well-enforced rights for outside investors. Finally, private control benefits are the benefits that insiders can gain from controlling a firm, which can include financial gains or other advantages that are not shared with other stakeholders @Leuz_2003.
3. While pulling the data for analysis, I encountered negative values for some key financial metrics such as operating income (`item1250`), net income before extraordinary items/preferred dividends (`item1551`), and net income before preferred dividends (`item1651`). The paper by @Leuz_2003 does not explicitly specify how to handle negative values in key financial metrics. For the purpose of this replication study, I will include negative values in the analysis. Including these values ensures that the analysis captures the full spectrum of earnings management activities across different countries.
4. Another potential source of discrepancies between the original and replicated tables may be the choice of variables pulled from Worldscope. For example, in the `wrds_ws_funda table`, both `item1151` and `item4051` are named “DEPRECIATION, DEPLETION AND AMORTIZATION” @WRDS_WS_Funda_2024. I chose `item1151` from the Income Statement rather than `item4051` from the Cash Flow Statement, based on the Excel Industrials Template by @WRDS_Balancing_Model_2024. Since the authors do not specify the choice of variables used from the database, this could cause differences in the results.
5. The EM measures are based on scaled variables (e.g., operating cash flow scaled by lagged total assets). As such, the currency of the relevant data items should not affect the results as long as the same currency is used consistently for both the numerator and the denominator. This approach ensures comparability across different countries, regardless of their local currencies. Additionally, according to a document by [@Thomson_Financial_2007, p.20], all Worldscope data is consistently reported in the local currency of each firm’s country of domicile, eliminating the need for currency conversions in this project.
333. ## delete. mine 
333. It is assumed that Penman (2013) restricted the possible P/B values to a range of 0 to 7 to exclude outliers. Hence, extreme P/B values that are negative and very high (greater than 7) are excluded to focus the analysis on firms with more stable and reasonable valuations, reducing the impact of outliers.

@@

To compile the dataset, the dynamic and static datasets were merged on the `item6105`  identifier, representing the unique Worldscope Permanent ID. WRDS advises using this identifier consistently within Worldscope data since it remains stable over time [@WRDS_Overview_2024]. An inner join was used for this merge, because this approach ensures that only the complete and consistent data from both tables is retained.

@@

As required by @Leuz_2003, financial institutions are excluded from the analysis based on their SIC codes. This is done by filtering out rows where the `item7021` identifier, representing the SIC code, falls within the range of 6000 to 6999. Hence, the dataset focuses only on non-financial companies, aligning with the methodology of the original paper.

@@

After retaining only relevant company data, excluding financial institutions, and focusing on specified countries, the processed data was then saved to a CSV file at the path `data/pulled` specified in the configuration file `config/pull_data_cfg​`.

## Step 2: Data Preparation
To prepare the data according to the methodology outlined in the paper, it is essential to follow specific steps. Firstly, countries with sufficient firm-year observations must be filtered. Each country should have at least 300 firm-year observations for certain key accounting variables, including total assets, sales, net income, and operating income. Secondly, firms with adequate consecutive data must be identified. Each firm must have income statement and balance sheet information for at least three consecutive years, where I focus on the same key variables as in the previous step.

@@

# Discretionary Accruals ##delete?

To demonstrate our workflow, we explore discretionary accruals across the U.S. We calculate modified Jones and Dechow and Dichev type accruals and show their distributional properties. The main purpose of all this, however, is to provide a toy use case for [our project template directory](https://github.com/trr266/project_template) that contains all the code to obtain the data, run the analysis and prepare a paper as well as a presentation.

Table \ref{tab:tab-descriptives-sample} presents our data that is based on a simple WRDS pull of Compustat data with financial firms (SIC 6XXX) excluded. We require data to calculate all variables and this drastically reduces the sample size. Modified Jones discretionary accruals are calculated loosely based on @HN_2007 and Dechow and Dichev discretionary accruals are calculated based on (big surprise) @DD_2002. As you will see from @fig-boxplot_smp, discretionary accruals are very noisy constructs, even after limiting the sample to observations with complete data and winsorizing all data to the top and bottom percentile for each year. @fig-scatter_dd_lnta shows a very prominent heteroscedasticity of discretionary accruals with regards to size. While researchers have tried to address this problem, the distributional properties of these constructs significantly complicate the interpretation of discretionary accrual-related findings. Especially in high powered settings, the measurement error, being highly correlated with size, will tend to load on variables that are unrelated to the underlying economic construct but correlated with size. Table \ref{tab:corr} shows some correlations and Table \ref{tab:reg} shows some completely pointless regressions.

@@

# Results
Cross-check your results with the original table to ensure accuracy. Compare your results with the results in the paper. If you notice differences, discuss where they may originate. Make sure to be as specific as possible. This could involve looking at the data selection, calculation methods, or any assumptions that might differ from the original; changes in the data over time, different interpretations of the methodology, or limitations in the data sources used. Consider whether the differences are significant and what they might mean for the conclusions drawn in the paper.

@@

Isn't that wonderful? Discretionary accruals rock but what rocks even more is open science and a collaborative workflow. Clone or fork this repository to kickstart your own projects. If you do not like either R or Python, consider contributing code in your favorite statistical programming language to the repo. Thanks for reading and enjoy!
gpt: Summarize the key findings and their significance.
This final assignment has required the comprehensive application of all skills learned and feedback received from previous assignments, making it a more complex project workflow.

@@

>>>>

# List of Abbreviations
\setlength{\parindent}{0em}

@@

The replicated table is shown below, followed by replication steps documentation, a detailed comparison, and discussion of the results.

## delete from fikir.
```{python}
#| echo: false
#| output: asis

@@

In addition, I impose the following assumptions to ensure clarity and consistency where the paper by @Leuz_2003 does not provide explicit guidance:

1. The original paper references the November 2000 version of the Worldscope Database. However, the data used for this analysis represents the latest available version, updated in July 2024, with quarterly frequency updates [@WRDS_2024]. Due to potential adjustments and updates made to the database since November 2000, there may be differences between the databases that could affect the results. For example, companies may restate financials after the original reporting period, so that these restatements are reflected in the later database version rather than the historical one. Moreover, the data vendor Refinitiv regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the November 2000 snapshot.
2. The original paper outlines key terms that will be used in this project to ensure consistency and accuracy in the replication. @Leuz_2003 define earnings management as the manipulation of a firm's reported economic performance by insiders to deceive certain stakeholders or to affect contractual results. Authors describe investor protection as a key institutional factor that limits insiders' acquisition of private control benefits, thereby reducing their incentives to manage accounting earnings by ensuring strong and well-enforced rights for outside investors. Finally, private control benefits are the benefits that insiders can gain from controlling a firm, which can include financial gains or other advantages that are not shared with other stakeholders @Leuz_2003.
3. While pulling the data for analysis, I encountered negative values for some key financial metrics such as operating income (`item1250`), or net income before preferred dividends (`item1651`). The paper by @Leuz_2003 does not explicitly specify how to handle negative values in key financial metrics. For the purpose of this replication study, I will include negative values in the analysis. Including these values ensures that the analysis captures the full spectrum of earnings management activities across different countries.
4. Another potential source of discrepancies between the original and replicated tables may be the choice of variables pulled from Worldscope. For example, in the `wrds_ws_funda table`, both `item1151` and `item4051` are named “DEPRECIATION, DEPLETION AND AMORTIZATION” @WRDS_WS_Funda_2024. I chose `item1151` from the Income Statement rather than `item4051` from the Cash Flow Statement, based on the Excel Industrials Template by @WRDS_Balancing_Model_2024. Since the authors do not specify the choice of variables used from the database, this could cause differences in the results.
5. The EM measures are based on scaled variables (e.g., operating cash flow scaled by lagged total assets). As such, the currency of the relevant data items should not affect the results as long as the same currency is used consistently for both the numerator and the denominator. This approach ensures comparability across different countries, regardless of their local currencies. Additionally, according to a document by [@Thomson_Financial_2007, p.20], all Worldscope data is consistently reported in the local currency of each firm’s country of domicile, eliminating the need for currency conversions in this project.
333. ## delete. mine 
333. It is assumed that Penman (2013) restricted the possible P/B values to a range of 0 to 7 to exclude outliers. Hence, extreme P/B values that are negative and very high (greater than 7) are excluded to focus the analysis on firms with more stable and reasonable valuations, reducing the impact of outliers.

@@

To ensure the integrity of the data, I filtered out rows with empty `item6105` (Worldscope Permanent ID) values, as this identifier is critical for firm/year level filtering in the data preparation step. In total, 125 observations from the dynamic data and 10,306 observations from the static data were removed. To compile the dataset, the dynamic and static datasets were merged on the `item6105` identifier, representing the unique Worldscope Permanent ID. WRDS advises using this identifier consistently within Worldscope data since it remains stable over time [@WRDS_Overview_2024]. An inner join was used for this merge, because this approach ensures that only the complete and consistent data from both tables is retained.

@@

As required by @Leuz_2003, financial institutions are removed from the analysis based on their SIC codes. This is done by filtering out rows where the `item7021` identifier, representing the SIC code, falls within the range of 6000 to 6999. Hence, the dataset focuses only on non-financial companies, aligning with the methodology of the original paper.

@@

After retaining only relevant company data, filtering out financial institutions, and focusing on specified countries, the processed data was then saved to a CSV file at the path `data/pulled` specified in the configuration file `config/pull_data_cfg​`.

## Step 2: Data Preparation
First, I checked the dataset for duplicate firm-year observations based on the combination of the Worldscope Permanent ID (`item6105`) and the fiscal year (`year_`) and confirmed that there were no duplicates present, ensuring the accuracy of the data for further analysis. As the original study does not specify the net income measure, `item1651` (Net Income before Preferred Dividends) was used as the variable for net income. This choice aligns with the final net income figure reported in the income statement, based on the Excel Industrials Template by @WRDS_Balancing_Model_2024.

To prepare the data sample in line with the methodology outlined in the paper, it is essential to follow the requirements, as instructed by @Leuz_2003. Firstly, countries with sufficient firm-year observations must be filtered. Each country should have at least 300 firm-year observations for certain key accounting variables, including total assets, sales, net income, and operating income. Secondly, firms with adequate consecutive data must be identified. Each firm must have income statement and balance sheet information for at least three consecutive years, where I focus on the same key variables as in the previous step. If a firm had at least three consecutive years of complete data at any point, all its data entries were retained in the final dataset.

@@

@@

# Results
##Cross-check your results with the original table to ensure accuracy. Compare your results with the results in the paper. If you notice differences, discuss where they may originate. Make sure to be as specific as possible. This could involve looking at the data selection, calculation methods, or any assumptions that might differ from the original; changes in the data over time, different interpretations of the methodology, or limitations in the data sources used. Consider whether the differences are significant and what they might mean for the conclusions drawn in the paper.

The replicated table shows some similarities with the original table by @Leuz_2003 in that . These findings are in line with valuation theory that .

However, the patterns are less clear in the replicated table (in particular ), which stands in contrast to @Leuz_2003.

@@

##gpt: Summarize the key findings and their significance. take results and insert them here

This project demonstrates the effectiveness of using an open science and collaborative workflow for analyzing earnings management measures across various countries. By following a step-by-step approach and using the TRR 266 Template for Reproducible Empirical Accounting Research, I was able to replicate an empirical table from @Leuz_2003 and provide insights into the trends of earnings management practices, which vary significantly across countries, similar to @Leuz_2003.

@@

The analysis revealed that

The replication yields mixed results. While

This final assignment has required the comprehensive application of all skills learned and feedback received from previous assignments, making it a more complex project workflow. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Thanks for reading!
